---
title: "W_UP_01"
author: "Chris Gonzalez"
date: "Summer 2023"
output: html_document
---



The report structure should include five sections.  see below



```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
mydata <- read.csv(file="pushups.csv")
```

# Introduction

<!--In this section you explain what you are trying to show. Where did the data come from? What is the research or other question you are trying to answer?!-->

Create an Rstudio project in your shared space on rstudio.cloud.  Using the dataset called pushups from the tigerstats package in R; answer the question posed by this null and alternate hypothesis in an html markdown document.

$H_0$: There is no difference between the average number of pushups of line vs skill players

$H_A$: The average number of pushups done by line players is statistically different than that of skill players.

# Methods

<!--Decide on your methods: use "variable analysis" or other appropriate descriptors. Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections: One for your descriptive results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here. Make sure to show your code. Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too. Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
library(ggplot2)

ggplot(mydata, aes(x = position, y = pushups)) +
  geom_boxplot() +
  labs(x = "Position", y = "Pushups") +
  ggtitle("Box Plot of Pushups by Position") +
  theme(plot.title = element_text(size = 20, hjust = 0.5))


```  
  
Based on the data the skill players where able to out perform the line players. The line players have less than 30 pushups vs the skilled players which overall did more than 30 pushups. With the box plot, the data is reflected on the x and y axis that can give the analysis a visual to the information collected.  



### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(pushups~position,data=mydata)
```
  
By taking numerical data of the min,median,mean we can see the skill players are out performing then the line players by the total number of pushups.


## Inferential Results

<!--State hypothesis clearly. Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc. Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
t.test(pushups~position,data=mydata)
```

With all the data analyzed via the box plot and numerical data, we can conclude that the skill players out performed the line players. This is shown in pushups with a 32.6 percent difference between the two means of the groups. 

# Discussion and Conclusion

<!--Discussion and conclusion here. If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason. Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
In Conclusion it is clear to confirm that the skill players have out performed the line players in pushups with about a 32.6% difference. This is proven with the use of box plots for a visual representation of the data and a numerical data broken down. 

